---
title: "Analyze Notes"
author: "Liang Zhang"
date: "2021-07-09"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(tidygraph)
library(ggraph)
library(patchwork)
library(lmerTest)
library(emmeans)
knitr::opts_knit$set(root.dir = here::here())
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

```{r load-data, include=FALSE}
targets::tar_load(graphs_euc)
targets::tar_load(mean_graphs_euc)
targets::tar_load(graphs_chi)
targets::tar_load(mean_graphs_chi)
targets::tar_load(file_child_viz_graph)
targets::tar_load(file_child_statistics)
```

```{r common-funs-config}
vis_graph <- function(g) {
  ggraph(g, layout = "igraph", algorithm = "circle") +
    geom_edge_link(aes(width = 1 / distance)) +
    geom_node_label(aes(label = name)) +
    scale_edge_width(range = c(0.1, 2), guide = "none") +
    theme_graph()
}
weights_type <- set_names(
  c("distance", "1 / distance"),
  c("Use Original Distance", "Use the Reciprocal of Distance")
)
```

# Using Euclidean Distance

## Graph for Each subject

Here we visualize the continuous graphs of each time point for each subject and each type of response form.

```{r}
graphs <- graphs_euc
src <- purrr::map_chr(
  sort(unique(graphs$SID)),
  ~ knitr::knit_expand(file_child_viz_graph, user = .x)
)
```

`r knitr::knit(text = str_c(src, collapse = "\n\n"))`

## Averaged Graph

This is the mean of all graphs.

### Written Form

```{r, fig.width=12, fig.height=8}
mean_graphs_euc |>
  filter(type == "w") |>
  mutate(plot = map(graph, vis_graph)) |>
  pull(plot) |>
  wrap_plots() +
  plot_annotation(tag_levels = "1", tag_prefix = "Time: ")
```

### Oral Form

```{r, fig.width=12, fig.height=8}
mean_graphs_euc |>
  filter(type == "o") |>
  mutate(plot = map(graph, vis_graph)) |>
  pull(plot) |>
  wrap_plots() +
  plot_annotation(tag_levels = "1", tag_prefix = "Time: ")
```

## Dynamic Graphs

```{r}
src <- purrr::imap_chr(
  weights_type,
  ~ knitr::knit_expand(
    file_child_statistics, 
    type_formula = .x,
    type_name = .y,
    context = "euc"
  )
)
```

`r knitr::knit(text = str_c(src, collapse = "\n\n"))`

# Using Chisquare Distance

## Graph for Each subject

Here we visualize the continuous graphs of each time point for each subject and each type of response form.

```{r}
graphs <- graphs_chi
src <- purrr::map_chr(
  sort(unique(graphs$SID)),
  ~ knitr::knit_expand(file_child_viz_graph, user = .x)
)
```

`r knitr::knit(text = str_c(src, collapse = "\n\n"))`

## Averaged Graph

This is the mean of all graphs.

### Written Form

```{r, fig.width=12, fig.height=8}
mean_graphs_chi |>
  filter(type == "w") |>
  mutate(plot = map(graph, vis_graph)) |>
  pull(plot) |>
  wrap_plots() +
  plot_annotation(tag_levels = "1", tag_prefix = "Time: ")
```

### Oral Form

```{r, fig.width=12, fig.height=8}
mean_graphs_chi |>
  filter(type == "o") |>
  mutate(plot = map(graph, vis_graph)) |>
  pull(plot) |>
  wrap_plots() +
  plot_annotation(tag_levels = "1", tag_prefix = "Time: ")
```

## Dynamic Graphs

```{r}
src <- purrr::imap_chr(
  weights_type,
  ~ knitr::knit_expand(
    file_child_statistics, 
    type_formula = .x,
    type_name = .y,
    context = "chi"
  )
)
```

`r knitr::knit(text = str_c(src, collapse = "\n\n"))`
